# Install taxize

```{r}
install_github('taxize_', 'ropensci') # uncomment to run
library(taxize)
```
	
*********
	
# Phylomatic - get a phylogeny of plant species
	
```{r}
# input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

# fetch the tree - the formatting of names and higher taxonmy is done within the function
tree <- phylomatic_tree(taxa=taxa, get = 'POST', informat='newick', method = "phylomatic", 
 		storedtree = "R20120829", taxaformat = "slashpath", outformat = "newick", clean = "true")

# plot the tree
plot(tree)
```
	
![phylogeny](URL)

*********
	
# Integrated Taxonomic Informaiton Service (ITIS)
	
# Search by term and search type (Note: TSN stands for Taxonomic Serial Number)

```{r}
itis(203539, c("getsynonymnamesfromtsn","getacceptednamesfromtsn"))
```
	
## Show higher taxonomy for a given TSN
	
```{r}
classification(685566, ID = "tsn")
```
	
## Get a TSN from a species name
	
```{r}
tsn <- get_tsn(searchterm = "Quercus_douglasii", searchtype = "sciname")

# use classification with get_tsn together:
classification(tsn)
```
	
*********
	
# NCBI Taxonomy Browser
	
## Get Unique Identifier
	
```{r}
uids <- get_uid(c("Chironomus riparius", "Chaetopteryx"))
```
	
	
## And retrieve classification
	
```{r}
classification(uids)
```
	

*********
	
# Global Names Resolver (GNR)
	
## Get just id's and names of sources in a data.frame
	
```{r}
tail(gnr_datasources(todf = T))
```
	
*********
	
## Give me the id for EOL (Encyclopedia of Life)
	
```{r}
out <- gnr_datasources(todf = T)
out[out$title == "EOL", "id"]
```
	
*********
	
## Fuzzy search for sources with the word "zoo"
	
```{r}
out <- gnr_datasources(todf = T)
outdf <- out[agrep("zoo", out$title, ignore.case = T), ]
outdf[1:2, ]
```
	
*********
	
## Resolve some names
	
### Search for _Helianthus annuus_ and _Homo sapiens_, return a data.frame
	
```{r}
gnr_resolve(names = c("Helianthus annuus", "Homo sapiens"), returndf = TRUE)[1:2, ]
```
	
*********
	
### Search for the same species, with only using data source 12 (i.e., EOL)
	
```{r}
gnr_resolve(names = c("Helianthus annuus", "Homo sapiens"), data_source_ids = "12", returndf = TRUE)
```
	
*********
# Tropicos: all Tropicos functions start with "tp_"
	
```{r}
head(tp_acceptednames(id = 25503923))
```
	
	
```{r}
head(tp_synonyms(id = 25509881))
```
	
*********
# uBio
	
## Search uBio using the namebank_search API method.
	
```{r}
ubio_namebank(searchName = "elephant", sci = 1, vern = 0)
```
	
```{r}
head(ubio_namebank(searchName = "Helianthus annuus", sci = 1, vern = 0)[,-c(2, 3)])
```
	
```{r}
out <- lapply(list("Helianthus debilis", "Astragalus aduncus"), function(x) ubio_namebank(searchName = x, sci = 1, vern = 0))
head(out[[2]][, -c(2, 3)])  # just Astragalus aduncus output
```
	
*********
	
# IUCN Red List
	
## Query the Red List API
	
```{r}
ia <- iucn_summary(c("Panthera uncia", "Lynx lynx"))
```
	
### Extract Status
	
```{r}
library(plyr)
laply(ia, function(x) x$status)
```